Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-11 manuscript/manuscript.tex
editing Ne section

which estimates the \vb{impact of selection} on allele frequency change between
the initial generation $0$ and some later generation $t$, which can be varied
to see how this quantity grows through time. When the sum of the covariances is
positive, this measure can intuitively be understood as the relative fraction
of allele frequency change normally thought of as ``drift" that is actually due
to selection. Additionally, $G(t)$ can be understood as a short-timescale
estimate of the reduction in neutral diversity due to linked selection (or
equivalently the reduction in neutral effective population size needed to
account linked selection, see Supplementary Materials Section
\ref{supp:reduction-approx}). Since \textcite{Barghi2019-qy} experiment is
sequenced every ten generations, in the numerator for the covariance we use the
allele frequency changes between adjacent timepoints, which are ten generations
apart; \vb{thus the strong covariances between adjacent generations are not
  observable and do not contribute to the numerator of $G(t)$}.
  \vb{Additionally, selection also inflates the variance in allele frequency
    change per generation; however, this effect cannot be easily distinguished
  from drift.} \vb{For both these reasons, our measure $G(t)$ is strongly
conservative} (\vb{we demonstrate this through simulations in Supplementary
Material Section \ref{supp:tempblocks}}).  Still, we find a remarkably strong
signal. Greater than $20\%$ of total, genome-wide allele frequency change over
60 generations is the result of selection (Figure \ref{fig:figure-1} B).

>>>>

which estimates the \vb{impact of selection} on allele frequency change between
the initial generation $0$ and some later generation $t$, which can be varied
to see how this quantity grows through time. When the sum of the covariances is
positive, this measure can intuitively be understood as the relative fraction
of allele frequency change normally thought of as ``drift" that is actually due
to selection. Additionally, $G(t)$ can be understood as a short-timescale
estimate of the reduction in neutral diversity due to linked selection (or
equivalently the reduction in neutral effective population size needed to
account linked selection, see Supplementary Materials Section
\ref{supp:reduction-approx}). Since \textcite{Barghi2019-qy} experiment is
sequenced every ten generations, in the numerator for the covariance we use the
allele frequency changes between adjacent timepoints, which are ten generations
apart; \vb{thus the strong covariances between adjacent generations are not
  observable and do not contribute to the numerator of $G(t)$}.
  \vb{Additionally, selection also inflates the variance in allele frequency
    change per generation; however, this effect cannot be easily distinguished
  from drift.} \vb{For both these reasons, our measure $G(t)$ is strongly
conservative} (\vb{we demonstrate this through simulations in Supplementary
Material Section \ref{supp:tempblocks}}).  Still, we find a remarkably strong
signal. Greater than $20\%$ of total, genome-wide allele frequency change over
60 generations is the result of selection (Figure \ref{fig:figure-1}
B). \gc{This proportion of variance attributable to selection builds
 over time in Figure \ref{fig:figure-1}B as the effects of
linked selection are compounded over the generations unlike genetic
drift. Our G(t) starts to plateau to a constant level as the
covariances from earlier generations have decayed and so no longer
contribute as strongly (Figure \ref{fig:figure-1}).}
